Biologically-Constrained 3D Agglomeration for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/1_related_work.tex
related work: categorize agglomeration

\subsubsection{Agglomeration}
Given the initial segmentation, some methods train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}.
Some methods rely solely on the accuracy of the predicted affinities and agglomerate hierarchically based on the mean affinity between supervoxels~\cite{lee2017superhuman,funke2017deep}.
Pape et al. present a scalable multicut algorithm to partition superpixels~\cite{beier2017multicut}.
\TODO{add learning-based algorithm} ~\cite{jain2011learning,bogovic2013learned}
%\subsubsection{Error-correction methods}
%Additional research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatic methods~\cite{rolnick2017morphological,error_correction_using_CNN}.
%However, to our knowledge, our method is the first to extract a 3D graph from an input segmentation for a true top-down\TODO{?} error correction approach. 
%This allows us to enforce domain-specific biology constraints and use efficient graph partitioning algorithms. 
% Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
% Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}. 
%We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted graph into the final neural reconstruction.

>>>>

\subsubsection{Agglomeration}
\TODO{rule-based method}
Some methods rely solely on the accuracy of the predicted affinities and agglomerate hierarchically based on the mean affinity between supervoxels~\cite{lee2017superhuman,funke2017deep}.

\TODO{classification-based method}
Given the initial segmentation, some methods train random-forest classifiers to produce the final segmentations~\cite{seymour2016rhoananet,nunez2014graph,parag2017anisotropic,zlateski2015image,10.1371/journal.pone.0125825}
extract different features
~\cite{jain2011learning,bogovic2013learned}.

\TODO{optimization-based method}
Pape et al. present a scalable multicut algorithm to partition superpixels~\cite{beier2017multicut}.

In our work, we combine classification and optimization.
%\subsubsection{Error-correction methods}
%Additional research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2014design,haehn2017guided,mojo2} or automatic methods~\cite{rolnick2017morphological,error_correction_using_CNN}.
%However, to our knowledge, our method is the first to extract a 3D graph from an input segmentation for a true top-down\TODO{?} error correction approach. 
%This allows us to enforce domain-specific biology constraints and use efficient graph partitioning algorithms. 
% Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
% Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}. 
%We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted graph into the final neural reconstruction.
